---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# ATE

<!-- badges: start -->
<!-- badges: end -->

The ATE (additive term extraction) package provides a variety of methods to estimate site, event, (and  path) terms from ground motion residuals.

## Installation

1. Make sure "tiydverse", "cmdstanr", "stringr","dplyr", "lme4", and "magrittr" are installed as they are dependencies. Otherwise, you can run the following command to install them. For error and warnings when installing "cmdstanr", please refer to the [page](https://mc-stan.org/cmdstanr/).

``` r
install.packages(c("tiydverse", "cmdstanr", "stringr","dplyr", "lme4", "magrittr"))
```

2. Install utility package “devtools”:
```r
install.packages("devtools")
```

3. Lastly, install “ATE” package:
```r
library(devtools)
install_github('gui33627/ATE')
```


## Example

This is the example code that reproduces the results of the simulation study in our paper:

```r
library(ATE)
N <- 100
num_event <- c(20, 50)
num_site <- c(40, 200)

# Simulation with balanced data
for (i in 1:length(num_event)) {

  results_list <- list()
  mse_results <- data.frame(matrix(NA, nrow = N, ncol = 4))

  for (j in 1:N) {
    # generate data
    gm_data <- dgp(num_event = num_event[i], num_site = num_site[i],
                   tau = 1, phi_S2S = 1, phi_SS = 1)

    delta_S2S_fixed <- ATE::stepwise_extraction(gm_data, random = FALSE)
    delta_S2S_random <- ATE::stepwise_extraction(gm_data, random = TRUE)
    delta_S2S_mixed <- ATE::mixed_extraction(gm_data)
    delta_S2S_bayesian <- ATE::bayesian_extraction(gm_data)


    results <- delta_S2S_fixed %>%
      left_join(delta_S2S_random, by = c("site_id" = "site_id")) %>%
      left_join(delta_S2S_mixed, by = c("site_id" = "site_id")) %>%
      left_join(delta_S2S_bayesian, by = c("site_id" = "site_id")) %>%
      rename(delta_S2S.fixed = delta_S2S.x, delta_S2S.random = delta_S2S.y,
             delta_S2S.mixed = delta_S2S.x.x, delta_S2S.bayesian = delta_S2S.y.y)

    mse <- gm_data %>% select(site_id, delta_S2S) %>% unique() %>% arrange(site_id) %>%
      left_join(results, by = c("site_id" = "site_id")) %>%
      mutate(y_fixed = delta_S2S.fixed - delta_S2S,
             y_random = delta_S2S.random - delta_S2S,
             y_mixed = delta_S2S.mixed - delta_S2S,
             y_bayesian = delta_S2S.bayesian - delta_S2S) %>%
      summarise(mse_fixed = sum((y_fixed)^2)/length(y_fixed),
             mse_random = sum((y_random)^2)/length(y_random),
             mse_mixed = sum((y_mixed)^2)/length(y_mixed),
             mse_bayesian = sum((y_bayesian)^2)/length(y_bayesian))

    results_list <- c(results_list, list(results))
    mse_results[j,] <- mse
    print(paste0(i," + ", j," done!"))
  }
  colnames(mse_results) <- colnames(mse)
  write.csv(mse_results, file = paste0("mse_results", i, ".csv"), row.names = FALSE)
}

# Simulation with unbalanced data
N <- 100
num_event <- c(20)
num_site <- c(40)
missingness <- c(0.1, 0.2)


for (k in 1:length(missingness)) {
  for (i in 1:length(num_event)) {

    results_list <- list()
    mse_results <- data.frame(matrix(NA, nrow = N, ncol = 4))

    for (j in 1:N) {
      # generate data
      gm_data <- dgp(num_event = num_event[i], num_site = num_site[i],
                     tau = 1, phi_S2S = 1, phi_SS = 1,
                     missing_percent = missingness[k])

      delta_S2S_fixed <- ATE::stepwise_extraction(gm_data, random = FALSE)
      delta_S2S_random <- ATE::stepwise_extraction(gm_data, random = TRUE)
      delta_S2S_mixed <- ATE::mixed_extraction(gm_data)
      delta_S2S_bayesian <- ATE::bayesian_extraction(gm_data)

      results <- delta_S2S_fixed %>%
        left_join(delta_S2S_random, by = c("site_id" = "site_id")) %>%
        left_join(delta_S2S_mixed, by = c("site_id" = "site_id")) %>%
        left_join(delta_S2S_bayesian, by = c("site_id" = "site_id")) %>%
        rename(delta_S2S.fixed = delta_S2S.x, delta_S2S.random = delta_S2S.y,
               delta_S2S.mixed = delta_S2S.x.x, delta_S2S.bayesian = delta_S2S.y.y)

      mse <- gm_data %>% select(site_id, delta_S2S) %>% unique() %>% arrange(site_id) %>%
        left_join(results, by = c("site_id" = "site_id")) %>%
        mutate(y_fixed = delta_S2S.fixed - delta_S2S,
               y_random = delta_S2S.random - delta_S2S,
               y_mixed = delta_S2S.mixed - delta_S2S,
               y_bayesian = delta_S2S.bayesian - delta_S2S) %>%
        summarise(mse_fixed = sum((y_fixed)^2)/length(y_fixed),
                  mse_random = sum((y_random)^2)/length(y_random),
                  mse_mixed = sum((y_mixed)^2)/length(y_mixed),
                  mse_bayesian = sum((y_bayesian)^2)/length(y_bayesian))

      results_list <- c(results_list, list(results))
      mse_results[j,] <- mse
      print(paste0(k, "+", i," + ", j," done!"))
    }
    colnames(mse_results) <- colnames(mse)
    write.csv(mse_results, file = paste0("mse_results",i, "_missing_", 
                                         missingness[k], ".csv"), row.names = FALSE)
  }
}

```
```{r, echo=FALSE}
mse_small <- read.csv("/Users/junhui/Library/CloudStorage/GoogleDrive-junhuiyang@umass.edu/My Drive/Pengfei/mixed_effect_simulation/sim_results/mse_results1.csv")
mse_large <- read.csv("/Users/junhui/Library/CloudStorage/GoogleDrive-junhuiyang@umass.edu/My Drive/Pengfei/mixed_effect_simulation/sim_results/mse_results2.csv")
mse_small_missing_0.1 <- read.csv("/Users/junhui/Library/CloudStorage/GoogleDrive-junhuiyang@umass.edu/My Drive/Pengfei/mixed_effect_simulation/sim_results/mse_results1_missing_unbalanced0.1.csv")
mse_small_missing_0.2 <- read.csv("/Users/junhui/Library/CloudStorage/GoogleDrive-junhuiyang@umass.edu/My Drive/Pengfei/mixed_effect_simulation/sim_results/mse_results1_missing_unbalanced0.2.csv")

mse_small <- mse_small[, -1]
mse_large <- mse_large[, -1]
mse_small_missing_0.1 <- mse_small_missing_0.1[, -1]
mse_small_missing_0.2 <- mse_small_missing_0.2[, -1]
```

```{r, eval=FALSE}
mse_small <- read.csv("mse_results1.csv")
mse_large <- read.csv("mse_results2.csv")
mse_small_missing_0.1 <- read.csv("mse_results1_missing_0.1.csv")
mse_small_missing_0.2 <- read.csv("mse_results1_missing_0.2.csv")
```

```{r}
colMeans(mse_small)
colMeans(mse_large)
colMeans(mse_small_missing_0.1)
colMeans(mse_small_missing_0.2)
```
The simulation results demonstrate that the Bayesian estimation of site terms consistently outperforms fixed, random, and mixed effect methods, achieving the lowest average MSE across all sites. This superior performance is observed in various scenarios, including small sample sizes, large sample sizes, and small samples with different percentages of missing data.

```{r}
plot_mse <- function(mse_mat, x_range = c(0, 0.2), y_range = c(0,30)){
  
  mse_x_range <- x_range
  mse_y_range <- y_range
  
  color_list <- c('black', 'red', 'blue', 'purple')
  plot(mse_x_range, mse_y_range, type = 'n', xlab = 'MSE', ylab = 'PDF')
  
  for (i in 1:ncol(mse_mat)) {
    lines(density(mse_mat[,i]), lwd = 2, col = color_list[i])
  }
  
  legend('topright', legend = colnames(mse_mat), col = color_list[1:ncol(mse_mat)], 
         lwd = 2, lty = 1)
}

plot_mse(mse_small)
```




